%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Senior Software Developer} % Job title
{ISC - Iran Science Citation Center} % Organization
{Shiraz, Iran} % Location
{Nov. 2014 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designed and implemented a coronavirus dashboard using HTML, JavaScript, Ajax, jQuery to offer a real-time window on a global pandemic and featured research publications. Provides updated data of COVID-19 statistics in the world on a daily basis.}
\item {Designed and implemented a real-time polling system using C\#, ASP.Net MVC, SQL Server, SignalR, Bootstrap Whether used for scheduling team meetings, business administration, or gathering opinions for managerial purposes. This reduced the voting process time in the company's management meetings by about 65\%.}
\item {Designed and implemented a university rankings ecosystem using C\#, ASP.Net MVC, SQL Server, Bootstrap, Windows Forms to assess university performance on the global stage and to provide a resource for readers to understand the different missions and efficiency of higher education institutions. This provided a systematic evaluation platform for over 2000 higher education institutions the world over.}
\item {Designed and implemented a university rankings ecosystem using C\#, ASP.Net MVC, SQL Server, Bootstrap, Windows Forms, WPF, Android, Java to assess university performance on the domestic stage and to provide a resource for readers to understand the different missions and efficiency of higher education institutions. This provided a systematic evaluation platform for over 200 higher education institutions in Iran and is the main Iranian source of evaluating scientific output.}
\item {Designed and implemented an interest free loan fund system using C\#, ASP.Net MVC, SQL Server, Bootstrap in a company with over 200 staff members that have helped them to handle their financial transactions and status with low latency and high reliability.}
\item {Designed and implemented a crawler using C\#, Windows Forms, Telerik, Oracle, Web Services to fetch automatically featured research publications on the free online databases. This decreased the data entry time from 1‑4 days to 1‑4 minutes and also reduced the number of associated staff from 20 to 3.}
\end{cvitems}
}

%------------------------------------------------    

\end{cventries}